---
title: "Weather data for Copenhagen"
author: "Mikkel Freltoft Krogsholm"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Weather data for Copenhagen}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette show you how to use the `norweather` package. 

`norweather` is  a wrapper for the weather forecasts from Yr, delivered by the Norwegian Meteorological Institute and the NRK.

Please read more about the conditions and guidelines at http://om.yr.no/verdata/
English explanation at http://om.yr.no/verdata/free-weather-data/

There are two steps to follow when you want to get the weather data:

* Find the place to get weather data for

* Get the weather data

## Find the place
In order for us to get the data from the Yr service we need to have the appropriate place url. There are several ways of doing this. 
 
**Manual lookup**    
You  can do a manual lookup on [yr.no](https://www.yr.no/). Here you can search for a location and navigate to the site with the weather forecast for that place. For instance, if you go to the webpage and search for *Copenhagen* and then navigate to the capital of Denmark you should end up on the following url: https://www.yr.no/place/Denmark/Capital/Copenhagen/

There you can se the weather forecast for Copenhagen, Denmark. You can also use the url to get data systematically into R.


**Automatic lookup**     
You can also use the `search_places()` function in the `norweather` package. 

```{r}
cph <- norweather::search_places(place = "Copenhagen")
```

This function searches for *Copenhagen* and then returns possible matches in a data frame.

```{r}
head(cph)
```

The first row looks about right, and indeed it is the same url as the one we identified above manually.

Now we can use the url to fetch weather data for automatically into R.

## Get the weather data

```{r}
place_url <- "https://www.yr.no/place/Denmark/Capital/Copenhagen/"
```


```{r}
forecast_days <- norweather::get_weather(place_url, forecast = "days")
```

```{r}
forecast_hours <- norweather::get_weather(place_url, forecast = "hours")
```

